Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
typo fix.
Wording

In other programming language communities,
behavior driven development (BDD) is getting much attention
slowly replacing test driven development (TDD).
In BDD, test code is written with specification terminology.
In other words, specification can be used for automatic testing.

In this paper, we consider how to put BDD into practice in Haskell.
We brought BDD methods from other programming language communities and
integrated them with a Haskell-original test method.
In particular, we introduced {\tt doctest}~\cite{doctest} and
integrated with QuickCheck~\cite{quickcheck}.
We also implemented {\tt Hspec} inspired by rspec~\cite{rspec}
and integrated with QuickCheck.

@@

\begin{quote}
\small
\begin{verbatim}
-- |
-- 'rev' @xs@ returns the elements of @xs@
-- in rev order. @xs@ must be finite.
--
-- >>> rev [1,2,3]
-- [3,2,1]
--
-- prop> rev [] == rev []
-- prop> rev (xs ++ ys) == rev ys ++ rev (xs::[Int])
-- prop> rev (rev xs) == (xs::[Int])

>>>>

In other programming language communities,
behavior driven development (BDD) is getting much attention, and is
slowly replacing test driven development (TDD).
In BDD, test code is written with specification terminology.
In other words, specification can be used for automatic testing.

In this paper, we explore how to apply BDD to Haskell.
We brought BDD methods from other programming language communities and
integrated them with a Haskell-original test method.
In particular, we introduced {\tt doctest}~\cite{doctest} and
integrated with QuickCheck~\cite{quickcheck}.
We also implemented {\tt Hspec} inspired by rspec~\cite{rspec}
and integrated with QuickCheck.

@@

\begin{quote}
\small
\begin{verbatim}
-- |
-- 'rev' @xs@ returns the elements of @xs@
-- in reverse order. @xs@ must be finite.
--
-- >>> rev [1,2,3]
-- [3,2,1]
--
-- prop> rev [] == rev []
-- prop> rev (xs ++ ys) == rev ys ++ rev (xs::[Int])
-- prop> rev (rev xs) == (xs::[Int])
